\documentclass[letterpaper,11pt]{article}


\input{helpers}
\begin{document}
\begin{justify}


  % HEADING SECTION STARTS HERE
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\large{Ray Chua}} $|$ {\href{mailto:raychua0106@gmail.com}{raychua0106@gmail.com}} $|$ {\href{}{\underline{stinkray77.github.io}}} & \textbf{Availability: }Mar 2026 onwards \\
    \href{https://linkedin.com/in/raychua0106/}{\underline{linkedin.com/in/raychua0106}} $|$ {\href{https://github.com/stinkray77}{\underline{github.com/stinkray77}}} $|$ {+65 9274 4840}
  \end{tabular*}
  % END OF SECTION %


  % EDUCATION SECTION STARTS HERE
  \section{Education}
  \resumeSubHeadingListStart

  \resumeSubheading{\textbf{National University of Singapore}}{Aug 2024 - May 2028}
  \resumeDescription{BComp in Computer Science, Minor in Mathematics, Minor in Quantitative Finance}
  \resumeItemListStart
  \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Software Engineering, Database Systems, Computer Networks, Programming Methodology, Quantitative Finance}
  \resumeItem{\textbf{Awards \& Leadership:} NUS Fintech Hackathon Finalist, TikTok TechJam 2025, Floorball Team Captain}
  \resumeItemListEnd

  \resumeSubHeadingListEnd
  % END OF SECTION %


  % EXPERIENCE SECTION STARTS HERE
  \section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading{\textbf{GetMarked $|$ \emph{Computational Linguistics \& AI Intern}}}{Dec. 2025 - Present}
  \resumeItemListStart
  \resumeItem{Engineered an end-to-end NLP content generation pipeline in Python, integrating the OpenRouter API to programmatically translate multi-dimensional linguistic constraints into structured pedagogical data.}
  \resumeItem{Built an automated idiom-detection microservice utilizing \texttt{sentence-transformers} and spaCy, processing over 10GB of raw unstructured phrases to classify literal versus figurative language.}
  \resumeItem{Implemented a robust data-validation layer utilizing custom JSON schemas, ensuring 100\% data integrity during programmatic ingestion into a centralized dictionary database of 10,000+ entries.}
  \resumeItemListEnd

  \resumeSubheading{\textbf{National University of Singapore} $|$ \emph{Teaching Assistant (CS2040S)}}{Jan. 2026 - Present}
  \resumeItemListStart
  \resumeItem{Facilitated weekly lab sessions and code reviews for 14 students, debugging Java implementations of advanced Data Structures and Algorithms.}
  \resumeItem{Mentored students on algorithmic optimization, time/space complexity trade-offs, Graph Theory (SSSP/MST), Dynamic Programming, and Amortized Analysis.}
  \resumeItemListEnd

  \resumeSubheading{\textbf{Sheares Hall Web Developers} $|$ \emph{Full Stack Developer}}{Aug 2024 - Jun 2025}
  \resumeItemListStart
  \resumeItem{Developed and deployed an internal administrative Next.js web application, serving over 500 residents and fully automating the manual hall point allocation process.}
  \resumeItem{Engineered a secure backend architecture integrating Firebase authentication and Supabase for real-time data storage and retrieval.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd
  % END OF SECTION %


  % PROJECTS SECTION STARTS HERE
  \section{Projects}
  \resumeSubHeadingListStart

  \resumeSubheading{\textbf{High-Performance Limit Order Book} $|$ \emph{C++}}{\href{https://github.com/stinkray77/Cpp-Limit-Order-Book}{GitHub}}
  \resumeItemListStart
  \resumeItem{Developed a high-performance trading engine in C++, implementing \texttt{std::map} data structures to manage the state of continuous Limit and Market orders.}
  \resumeItem{Engineered robust memory management protocols using smart pointers, eliminating memory leaks during continuous, high-throughput data ingestion.}
  \resumeItem{Reduced p99 execution latency to $\sim$117ns by applying \texttt{-O3} compiler optimizations and structuring CPU-native architecture builds.}
  \resumeItemListEnd

  \resumeSubheading{\textbf{SG Internships Automated Scraper} $|$ \emph{Python, PostgreSQL}}{\href{https://github.com/stinkray77/sg-internship-scraper}{GitHub}}
  \resumeItemListStart
  \resumeItem{Built a serverless Python ETL pipeline utilizing REST APIs and BeautifulSoup to aggregate unstructured JSON and HTML payloads from 5+ job boards and ATS endpoints.}
  \resumeItem{Deployed automated hourly GitHub Actions workflows, engineering a PostgreSQL database for deduplication and integrating the Telegram API for real-time mobile alerts.}
  \resumeItemListEnd

  \resumeSubheading{\textbf{GradWise Academic Planning App} $|$ \emph{React, Node.js, MongoDB}}{\href{https://github.com/nicho369/orbital}{GitHub}}
  \resumeItemListStart
  \resumeItem{Designed and deployed a full-stack web application enabling students to interactively optimize their university academic planning.}
  \resumeItem{Implemented secure authentication protocols and dynamic data visualizations, reducing client-side load times through reactive data rendering.}
  \resumeItemListEnd

  \resumeSubHeadingListEnd
  % END OF SECTION %

  % AWARDS SECTION STARTS HERE
  % \section{Awards}
  %   \resumeSubHeadingListStart
  %     \resumeProjectHeading{\textbf{NUS Hack\&Roll `25} - \emph{Top 8} $|$ \textbf{NUS-ISE Micron BACC `24} - \emph{2nd Runner-up} $|$ \textbf{Ground Zero `24} - \emph{Top 10}}{}
  %     \resumeProjectHeading{\textbf{SCS Splash Awards `23} - \emph{1st} $|$ \textbf{SUTD WhatTheHack `23} - \emph{1st} $|$ \textbf{HTX HacX! `23} - \emph{3rd} $|$ \textbf{CloudHacks `23} - \emph{1st}}{}
  %   \resumeSubHeadingListEnd
  % END OF SECTION %


  % TECHNICAL SKILLS SECTION STARTS HERE
  \section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]\small{\item{
          \textbf{Languages: }{Python, Java, C/C++, JavaScript, SQL, HTML, CSS} \\
          \textbf{Frameworks: }{React, Node.js, Next.js, JUnit 5, JavaFX} \\
          \textbf{Developer Tools: }{Git, Docker, PostgreSQL, MongoDB, Firebase, Supabase, GitHub Actions} \\
          \textbf{Libraries: }{\texttt{sentence-transformers}, spaCy, BeautifulSoup4, pandas, NumPy}
          }}
  \end{itemize}
  % END OF SECTION %


  % END OF DOCUMENT
\end{justify}
\end{document}
