\documentclass[letterpaper,11pt]{article}


\input{helpers}
\begin{document}
\begin{justify}


    % HEADING SECTION STARTS HERE
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\large{Ray Chua}} $|$ {\href{mailto:raychua0106@gmail.com}{raychua0106@gmail.com}} $|$ {\href{https://stinkray77.github.io}{\underline{stinkray77.github.io}}} & \textbf{Availability: }Mar 2026 onwards \\
        \href{https://linkedin.com/in/raychua0106/}{\underline{linkedin.com/in/raychua0106}} $|$ {\href{https://github.com/stinkray77}{\underline{github.com/stinkray77}}} $|$ {+65 9274 4840}
    \end{tabular*}
    % END OF SECTION %


    % EDUCATION SECTION STARTS HERE
    \section{Education}
    \resumeSubHeadingListStart

    \resumeSubheading{\textbf{National University of Singapore}}{Aug 2024 - May 2028}
    \resumeDescription{BComp in Computer Science, Minor in Mathematics, Minor in Quantitative Finance}
    \resumeItemListStart
    \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Software Engineering, Database Systems, Computer Networks, Programming Methodology, Quantitative Finance}
    \resumeItem{\textbf{Awards \& Leadership:} NUS Fintech Hackathon Finalist, TikTok TechJam 2025, Floorball Team Captain}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
    % END OF SECTION %


    % EXPERIENCE SECTION STARTS HERE
    \section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading{\textbf{GetMarked $|$ \emph{Computational Linguistics \& AI Intern}}}{Dec. 2025 - Present}
    \resumeItemListStart
    \resumeItem{Engineered an end-to-end NLP content generation pipeline in Python, integrating the OpenRouter API to programmatically translate multi-dimensional linguistic constraints into structured pedagogical data.}
    \resumeItem{Built an automated idiom-detection microservice utilizing \texttt{sentence-transformers} and spaCy, processing over 10GB of raw unstructured phrases to classify literal versus figurative language.}
    \resumeItem{Implemented a robust data-validation layer utilizing custom JSON schemas, ensuring 100\% data integrity during programmatic ingestion into a centralized dictionary database of 10,000+ entries.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{National University of Singapore} $|$ \emph{Teaching Assistant (CS2040S)}}{Jan. 2026 - Present}
    \resumeItemListStart
    \resumeItem{Mentored 14 students on Java-based algorithmic optimization, debugging complex implementations of Graph Theory (SSSP/MST) and Dynamic Programming to improve code efficiency.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{Sheares Hall Web Developers} $|$ \emph{Full Stack Developer}}{Aug 2024 - Jun 2025}
    \resumeItemListStart
    \resumeItem{Built a Next.js administrative platform for 500+ residents, automating hall point allocation via Firebase Auth and Supabase real-time data synchronization}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
    % END OF SECTION %


    % PROJECTS SECTION STARTS HERE
    \section{Projects}
    \resumeSubHeadingListStart

    \resumeSubheading{\textbf{AlphaStream $|$ Distributed Trading Microservices} $|$ \emph{C++, Python, Docker}}{\href{https://github.com/stinkray77/AlphaStream}{GitHub}}
    \resumeItemListStart
    \resumeItem{Architected a distributed microservices pipeline decoupling a high-latency NLP inference service (Python) from a high-performance execution engine (C++) via \textbf{ZeroMQ} asynchrony.}
    \resumeItem{Integrated \textbf{FinBERT (LLM)} via Hugging Face to process real-time financial news streams, implementing a robust error-handling layer to manage WebSocket lifecycle and unauthenticated API rate limits.}
    \resumeItem{Orchestrated a containerized ecosystem using \textbf{Docker Compose}, utilizing \textbf{multi-stage builds} to minimize image sizes and resolving \textbf{GLIBC ABI} compatibility issues for cross-platform deployment.}
    \resumeItem{Implemented defensive C++ serialization using \texttt{nlohmann/json}, including pattern-matching logic to validate signal integrity and prevent runtime crashes from malformed network packets.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{High-Performance Limit Order Book} $|$ \emph{C++}}{\href{https://github.com/stinkray77/Cpp-Limit-Order-Book}{GitHub}}
    \resumeItemListStart
    \resumeItem{Engineered a high-throughput matching engine using optimized STL containers and smart pointers, ensuring memory safety and $O(\log N)$ matching complexity for continuous order streams.}
    \resumeItem{Reduced p99 execution latency to \textbf{$\sim$117ns} through \texttt{-O3} compiler flag optimization and CPU-native builds to maximize instruction-level parallelism.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{SG Internships Automated Scraper} $|$ \emph{Python, PostgreSQL}}{\href{https://github.com/stinkray77/sg-internship-scraper}{GitHub}}
    \resumeItemListStart
    \resumeItem{Built a serverless Python ETL pipeline utilizing REST APIs and BeautifulSoup to aggregate unstructured JSON and HTML payloads from 5+ job boards and ATS endpoints.}
    \resumeItem{Deployed automated hourly GitHub Actions workflows, engineering a PostgreSQL database for deduplication and integrating the Telegram API for real-time mobile alerts.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{GradWise Academic Planning App} $|$ \emph{React, Node.js, MongoDB}}{\href{https://github.com/nicho369/orbital}{GitHub}}
    \resumeItemListStart
    \resumeItem{Designed and deployed a full-stack web application enabling students to interactively optimize their university academic planning.}
    \resumeItem{Implemented secure authentication protocols and dynamic data visualizations, reducing client-side load times through reactive data rendering.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
    % END OF SECTION %

    % AWARDS SECTION STARTS HERE
    % \section{Awards}
    %   \resumeSubHeadingListStart
    %     \resumeProjectHeading{\textbf{NUS Hack\&Roll `25} - \emph{Top 8} $|$ \textbf{NUS-ISE Micron BACC `24} - \emph{2nd Runner-up} $|$ \textbf{Ground Zero `24} - \emph{Top 10}}{}
    %     \resumeProjectHeading{\textbf{SCS Splash Awards `23} - \emph{1st} $|$ \textbf{SUTD WhatTheHack `23} - \emph{1st} $|$ \textbf{HTX HacX! `23} - \emph{3rd} $|$ \textbf{CloudHacks `23} - \emph{1st}}{}
    %   \resumeSubHeadingListEnd
    % END OF SECTION %


    % TECHNICAL SKILLS SECTION STARTS HERE
    \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]\small{\item{
              \textbf{Languages: }{Python, Java, C/C++, JavaScript, SQL, HTML, CSS} \\
              \textbf{Frameworks: }{React, Next.js, Node.js, \textbf{ZeroMQ}, JUnit 5, PyTorch} \\
              \textbf{Developer Tools: }{Git, \textbf{Docker (Compose/Multi-stage)}, PostgreSQL, AWS, GitHub Actions, Linux/Bash} \\
              \textbf{Libraries: }{\textbf{Hugging Face Transformers}, pandas, NumPy, spaCy, BeautifulSoup4}
              }}
    \end{itemize}
    % END OF SECTION %


    % END OF DOCUMENT
\end{justify}
\end{document}
