\documentclass[letterpaper,11pt]{article}


\input{helpers}
\begin{document}
\begin{justify}


    % HEADING SECTION STARTS HERE
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{\large{Ray Chua}} $|$ {\href{mailto:raychua0106@gmail.com}{raychua0106@gmail.com}} $|$ {\href{https://stinkray77.github.io}{\underline{stinkray77.github.io}}} & \textbf{Availability: }Mar 2026 onwards \\
        \href{https://linkedin.com/in/raychua0106/}{\underline{linkedin.com/in/raychua0106}} $|$ {\href{https://github.com/stinkray77}{\underline{github.com/stinkray77}}} $|$ {+65 9274 4840}
    \end{tabular*}
    % END OF SECTION %


    % EDUCATION SECTION STARTS HERE
    \section{Education}
    \resumeSubHeadingListStart

    \resumeSubheading{\textbf{National University of Singapore}}{Aug 2024 - May 2028}
    \resumeDescription{BComp in Computer Science, Minor in Mathematics, Minor in Quantitative Finance}
    \resumeItemListStart
    \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Software Engineering, Database Systems, Computer Networks, Programming Methodology, Quantitative Finance}
    \resumeItem{\textbf{Awards \& Leadership:} NUS Fintech Hackathon Finalist, TikTok TechJam 2025, Floorball Team Captain}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
    % END OF SECTION %


    % EXPERIENCE SECTION STARTS HERE
    \section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading{\textbf{GetMarked $|$ \emph{Computational Linguistics \& AI Intern}}}{Dec. 2025 - Present}
    \resumeItemListStart
    \resumeItem{Architected a statistical sampling algorithm utilizing NumPy and wordfreq to optimize the distribution of linguistic
        attributes, scaling the pedagogical database to 10,000+ benchmarked entries.}
    \resumeItem{Engineered a vector-space classification model using Cosine Similarity and sentence-transformers to mathemati-
        cally filter a 10GB raw phrase dataset based on semantic proximity.}
    \resumeItem{Optimized large-scale data processing workflows using pandas for vector-based similarity searches, significantly re-
        ducing computational overhead during high-dimensional semantic comparisons.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{National University of Singapore} $|$ \emph{Teaching Assistant (CS2040S)}}{Jan. 2026 - Present}
    \resumeItemListStart
    \resumeItem{Facilitated weekly lab sessions and code reviews for 14 students, debugging Java implementations of advanced Data
        Structures and Algorithms.}
    \resumeItem{Mentored students on algorithmic optimization, time/space complexity trade-offs, Graph Theory (SSSP/MST), Dy-
        namic Programming, and Amortized Analysis.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{Sheares Hall Web Developers} $|$ \emph{Full Stack Developer}}{Aug 2024 - Jun 2025}
    \resumeItemListStart
    \resumeItem{Developed and deployed an internal administrative Next.js web application, serving over 500 residents and fully
        automating the manual hall point allocation process.}
    \resumeItem{Engineered a secure backend architecture integrating Firebase authentication and Supabase for real-time data storage
        and retrieval.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
    % END OF SECTION %


    % PROJECTS SECTION STARTS HERE
    \section{Projects}
    \resumeSubHeadingListStart

    \resumeSubheading{\textbf{AlphaStream $|$ Distributed AI Trading Pipeline} $|$ \emph{C++, Python, ZeroMQ}}{\href{https://github.com/stinkray77/AlphaStream}{GitHub}}
    \resumeItemListStart
    \resumeItem{Engineered a distributed microservices pipeline utilizing \textbf{ZeroMQ (PUB/SUB)} for sub-millisecond inter-process communication between a Python-based AI inference layer and a C++ matching engine.}
    \resumeItem{Integrated \textbf{FinBERT (Transformer LLM)} via Hugging Face to perform real-time NLP sentiment analysis on live Alpaca API news feeds, automating trade signal generation based on calculated scoring vectors.}
    \resumeItem{Optimized inference latency on Apple Silicon using \textbf{MPS (Metal Performance Shaders)} and \textbf{Accelerate}, ensuring high-throughput signal processing during high-volatility market events.}
    \resumeItem{Dockerized the full-stack architecture using multi-stage builds and resolved \textbf{GLIBC/ABI} compatibility issues to ensure binary portability across distributed environments.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{High-Performance Limit Order Book} $|$ \emph{C++}}{\href{https://github.com/stinkray77/Cpp-Limit-Order-Book}{GitHub}}
    \resumeItemListStart
    \resumeItem{Developed an ultra-low latency matching engine in C++ implementing \texttt{std::map} to strictly enforce price-time priority for Limit and Market orders.}
    \resumeItem{Reduced p99 execution latency to \textbf{$\sim$117ns} by applying \texttt{-O3} compiler optimizations and structuring CPU-native architecture builds to minimize cache misses.}
    \resumeItemListEnd

    \resumeSubheading{\textbf{SG Internships Automated Scraper} $|$ \emph{Python, PostgreSQL}}{\href{https://github.com/stinkray77/sg-internship-scraper}{GitHub}}
    \resumeItemListStart
    \resumeItem{Built a serverless Python ETL pipeline utilizing REST APIs and BeautifulSoup to aggregate unstructured JSON and HTML payloads from 5+ job boards and ATS endpoints.}
    \resumeItem{Deployed automated hourly GitHub Actions workflows, engineering a PostgreSQL database for deduplication and integrating the Telegram API for real-time mobile alerts.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd
    % END OF SECTION %

    % AWARDS SECTION STARTS HERE
    % \section{Awards}
    %   \resumeSubHeadingListStart
    %     \resumeProjectHeading{\textbf{NUS Hack\&Roll `25} - \emph{Top 8} $|$ \textbf{NUS-ISE Micron BACC `24} - \emph{2nd Runner-up} $|$ \textbf{Ground Zero `24} - \emph{Top 10}}{}
    %     \resumeProjectHeading{\textbf{SCS Splash Awards `23} - \emph{1st} $|$ \textbf{SUTD WhatTheHack `23} - \emph{1st} $|$ \textbf{HTX HacX! `23} - \emph{3rd} $|$ \textbf{CloudHacks `23} - \emph{1st}}{}
    %   \resumeSubHeadingListEnd
    % END OF SECTION %


    % TECHNICAL SKILLS SECTION STARTS HERE
    \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]\small{\item{
              \textbf{Languages: }{Python, Java, C/C++, JavaScript, SQL, HTML, CSS} \\
              \textbf{Frameworks: }{React, Node.js, Next.js, JUnit 5, JavaFX} \\
              \textbf{Developer Tools: }{Git, \textbf{Docker (Compose/Multi-stage)}, PostgreSQL, AWS, GitHub Actions, Linux/Bash} \\
              \textbf{Libraries: }{\textbf{PyTorch, Hugging Face Transformers, ZeroMQ (libzmq)}, pandas, NumPy, spaCy} \\              }}
    \end{itemize}
    % END OF SECTION %


    % END OF DOCUMENT
\end{justify}
\end{document}
